\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-11-26 icra-2021.tex
ach changed that intro again

Many scenarios involving unmanned aerial vehicles (UAVs), such as precision agriculture, search and rescue, and surveillance, require high autonomy but have limited energy budgets. A typical example of a mission in these scenarios is a UAV flying a trajectory and performing some on-board computational tasks with little human interaction. For instance, the UAV might detect ground patterns and inform other ground-based actors. We refer to the computational tasks that can be dynamically replanned as computations. We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the trajectory, computations, and energy requirements. Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware. They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}. Such a state of practice has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs. The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.

@@

Unlike most of the past planning algorithms literature, our algorithm plans both the computations and the trajectory. We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory. The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}. To express the trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE). We plan the computations using a modeling tool presented in our previous work~\cite{seewald2019coarse}. In our approach, the user specifies an initial mission plan--the TEEs,  computations, energy budget, and some parameters. The parameters are the maximum, minimum, and current levels of the computations and trajectory. The energy budget is the battery capacity and some other battery parameters. The algorithm replans the initial mission plan as the remaining battery state of charge (SoC) unexpectedly changes due to, e.g., atmospheric interferences. Our goal is to complete the mission with the highest possible current computations and trajectory parameters as the UAV flies and its batteries drain. In the remainder of the paper, we adopt the following notation. We refer to the current computations and trajectory parameters simply as computations and trajectory parameters. We refer to parameters when we deal with both. We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets. There can be multiple or none computations sets per each task, and the same applies to the trajectory. The term parameters is not to be confused with the battery parameters, which we always mention explicitly. These are fixed values that are not replanned by the algorithm.

To achieve the dynamic mission planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference). Mission periodicity is often present due to the mission's repetitive patterns~\cite{seewald2020mechanical}. Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue). Given that the mission is periodic, we expect the energy to approximately evolve periodically. 
The observation applies broadly; we show how many UAV scenarios have a repetitive energy evolution. Moreover, we briefly investigate these patterns in some ground-based mobile robots. We use Fourier analysis to derive the model, and state estimation to address the uncertainty. The algorithm outputs the parameters using output model predictive control (MPC).

>>>>

Often, unmanned aerial vehicle (UAV) planning algorithms generate a trajectory. We are interested in a different algorithm: one that plans a UAV mission. In such a mission, the UAV has to fly an assigned path--which can be composed of many trajectories--and compute some on-board computational tasks. Many scenarios involving UAVs, such as precision agriculture, search and rescue, and surveillance, necessitates mission planning, and are energy critical. For instance, the UAV might detect ground patterns and inform other ground-based actors with little human interaction. We refer to the computational tasks that can be dynamically replanned as computations. We are interested in energy-aware dynamic mission planning, which would find optimal tradeoffs between the path, computations, and energy requirements. The UAV can deviate from the path and change the computations within user-defined constraints. Current generic planning solutions for outdoor UAVs do not plan the mission dynamically, nor are energy-aware. They are often semi-autonomous; the mission is static and usually defined using mission planning software~\cite{daponte2019review}. It is such a state of practice that has prompted us to propose an \emph{energy-aware dynamic mission planning algorithm} for UAVs. The algorithm combines and generalizes some of the past body of knowledge on mobile robot planning problems and addresses the increasing \emph{computational demands} and their relation to energy consumption, path, and autonomy for the UAV mission planning problem.

@@

Unlike most of the past planning algorithms literature, our algorithm plans both the computations and the trajectory. We guide the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory. The use of vector fields for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}. To express the trajectory, we use a mathematical function that we refer to as the trajectory explicit equation (TEE). We plan the computations using a modeling tool presented in our previous work~\cite{seewald2019coarse}. In our approach, the user specifies an initial mission plan--the TEEs,  computations, energy budget, and some parameters. The parameters are the maximum, minimum, and current levels of the computations and trajectory. The energy budget is the battery capacity and some other battery parameters. The algorithm replans the initial mission plan as the remaining battery state of charge (SoC) unexpectedly changes due to, e.g., atmospheric interferences. Our goal is to complete the mission with the highest possible current computations and trajectory parameters as the UAV flies and its batteries drain. In the remainder of the paper, we adopt the following notation. We refer to the current computations and trajectory parameters simply as computations and trajectory parameters. We refer to parameters when we deal with both. We refer to the constraints sets that delimit the maximum and minimum level of parameters as computations sets and trajectory sets. There can be multiple or none computations sets per each task, and the same applies to the trajectory. The term parameters is not to be confused with the battery parameters, which we always mention explicitly. These are fixed values that are not replanned by the algorithm. The algorithm outputs the parameters using output model predictive control (MPC).

To achieve the dynamic mission planning, we further introduce and formally proof a periodic energy model that accounts for the uncertainty (atmospheric interference). We use Fourier analysis to derive the model, and state estimation to address the uncertainty. Mission periodicity is often present due to the mission's repetitive patterns~\cite{seewald2020mechanical}. Indeed UAV scenarios often iterate over a set of tasks and trajectories (e.g., monitoring or search and rescue). Given that the mission is periodic, we expect the energy to approximately evolve periodically. 
The observation applies broadly; we show different UAV scenarios with periodic energy signals. Moreover, we briefly investigate such signals in some ground-based mobile robots.
